--- 
always_allow_html: yes
editor_options:
  chunk_output_type: console
output:
  html_document:
    df_print: paged
---

```{r make-kc-lookup-excel-doc-setup, include = FALSE}
library(tidyverse)
library(stringr)
library(sf)
library(googledrive)
library(miscgis)
library(forcats)
library(leaflet)
library(mapview)
library(miscgis)
library(htmltools)
library(snakecase)
library(magrittr)
library(rprojroot)
library(knitr)

root <- rprojroot::is_rstudio_project
root_file <- root$make_fix_file()
options(httr_oob_default=TRUE) 
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

### Lookup Table Categorical Features

####Description {-}

King County provides a Lookup Table to decode features from the Assesor datasets and this analysis makes use of the following features from that Table:

  - Present Use
  - _add others here_


####Links: {-}
  - [Source <i class="fa fa-external-link"></i>](http://info.kingcounty.gov/assessor/DataDownload/default.aspx)
  - [Data <i class="fa fa-download"></i>](http://aqua.kingcounty.gov/extranet/assessor/Lookup.zip) 

#### Processing Steps {-}
##### Summary {-}
  1. Create `lu`: A `tibble` object containing the King County Lookup document information.
  2. Create `pu` (_add others here_): Filter `lu` by `LU_TYPE` to select a single lookup category, then exact `LU_DESCRIPTION` and `LU_ITEM` in a named vector object.
  3. Upload each object to Drive.
  
##### Step 1 {-}
```{r make-kc-lookup-excel-doc-01, echo = TRUE, message=FALSE}

lu_fp <- root_file("./1-data/2-external/EXTR_LookUp.csv")

lu <- 
  make_or_read(lu_fp,
               {
                 dr_id <- as_id("0B5Pp4V6eCkhrSThkY055LUdxakE")
                 
                 drive_read(dr_id = dr_id,
                            path = lu_fp,
                            read_fun = read_csv,
                            .tempfile = FALSE,
                            progress = FALSE)
               },
               {read_csv(lu_fp,progress = FALSE)})

```


##### Step 2 {-}
```{r make-kc-lookup-excel-doc-02, echo = TRUE}

# PRESENT USE
pu <- 
  lu %>%
  rename_all(to_screaming_snake_case) %>% 
  filter(LU_TYPE %in% 102) %>% 
  select(LU_DESCRIPTION, LU_ITEM) %>% 
  pmap(~purrr::set_names(..1,..2)) %>% 
  unlist

data.frame(DESCRIPTION = pu) %>% kable(format = "html")

```

##### Step 3 {-}

```{r make-kc-lookup-excel-doc-03, eval = FALSE, echo = TRUE}

args_df <- 
  tribble( 
    ~ obj,               ~ name,
       pu, "kc-present-use.rds"           
  )

save_and_upload <- function(obj, name){
 
  folder <- as_id("0B5Pp4V6eCkhrZ3NHOEE0Sl9FbWc")
 
  tmp <- tempfile()

  write_rds(obj,tmp)

  drive_upload(tmp, folder, name = name)
   
}

pmap(args_df, ~ save_and_upload(..1,..2)) 

```

