---
title: 'EDA: Lot Size Outliers'
output:
  html_document:
    df_print: paged
---

### Overview

This is an exploratory analysis of the parcel size (`PARCEL_AREA`) and parcel size ratio (`PARCEL_AREA_RATIO`) fields.

The focus questions for this exploration are:

  * Q1
  * Q2
  * Q3

```{r setup, include=FALSE }

source(here::here("2-communication/1-rscripts/01-drake-setup.R"))
source(here("2-communication/1-rscripts/02-drake-functions.R"))

library(skimr)
library(visdat)
library(mapview)
library(patchwork)

Sys.setlocale("LC_CTYPE", "Chinese")
theme_set(theme_bw())

```

```{r load-objects, include=FALSE}

loadd(inventory)
loadd(parcel_sf_ready) 


```

### Setup

Create the `inv` object that will be used to explore the data and provide answers to the questions above:

```{r make-inv}

sf <- c("Single-Family Residential")
mf <- c("General Mixed Use", "Multi-Family Residential", "Mixed Use Commercial/Residential")

inv <- inventory %>% 
  st_drop_geometry() %>% 
  transmute(PIN, 
            SUITABLE_LGL,
            SUITABLE = if_else(SUITABLE_LGL, "suitable", "not") %>% factor() %>% fct_rev,
            NEW_SUITABLE_LGL = SUITABLE_OWNER_LGL & SUITABLE_WATER_OVERLAP_LGL & SUITABLE_WITHIN_UGA_LGL & SUITABLE_ZONING_CONSOL_20_LGL & SUITABLE_PRESENT_USE_LGL,
         PROPERTY_NAME, 
         OWNER_CATEGORY, 
         ZONING = SUIT_ZONING_CONSOL_20,
         ZONING_TYPE = case_when(
           ZONING %in% sf ~ "single family",
           ZONING %in% mf ~ "multi-family",
           TRUE ~ "other"
         ) %>% factor(levels = c("single family", "multi-family", "other")),
         SUIT_PARCEL_AREA = as.double(SUIT_PARCEL_AREA),  
         SUIT_PARCEL_AREA_OUTLIER = is_outlier(sqrt(SUIT_PARCEL_AREA)),
         SUIT_PARCEL_AREA_RATIO,
         SUIT_PARCEL_AREA_RATIO_OUTLIER = is_outlier(SUIT_PARCEL_AREA_RATIO),
         AREA_CITY_BLOCK = if_else(SUIT_PARCEL_AREA >= .75,"greater than a block","less than a block","less than a block") %>% factor() %>% fct_rev(),
         AREA_CITY_BLOCK_DETAIL = cut(SUIT_PARCEL_AREA, 
                                      breaks=c(-Inf, 0.1, 0.378, .75, 1.5, Inf ), 
                                      labels=c("under-sized","quarter-block","half-block", "whole-block", "over-sized")),
         BLDG_LGL = if_else(BLDG_NBR>1,TRUE,FALSE,FALSE),
         BDLG_FCT = BLDG_NBR %>% 
           factor(ordered = TRUE) %>% 
           fct_explicit_na(0) %>% 
           fct_lump(n = 4,  other_level = "more than 3") %>% 
           fct_relevel(c("0","1","2","3","more than 3")))

```

```{r explore-parcel-area-glimpse}
glimpse(inv)

skim(inv)
```


### Histograms

```{r explore-parcel-area-hist, message = FALSE}

gg1 <- ggplot(data = inv, mapping = aes(x = SUIT_PARCEL_AREA))
gg1 <- gg1 + geom_histogram() 
gg1 <- gg1 + facet_wrap(~ BDLG_FCT, scales = "free")  
gg1

```





### 2d Density: parcel area x area ratio x number of buildings

```{r explore-parcel-area-2d-density, message = FALSE}

gg2 <- ggplot(data = inv, mapping = aes(x = SUIT_PARCEL_AREA, y = SUIT_PARCEL_AREA_RATIO))
gg2 <- gg2 + geom_bin2d()
gg2 <- gg2 + geom_density2d(color = "orange", alpha = .25)
gg2 <- gg2 + scale_x_sqrt() 
gg2 <- gg2 + facet_wrap(~BDLG_FCT, nrow = 1)
gg2 <- gg2 + coord_fixed(25) 
gg2

```




### What about the zoning divide?

Exploratory questions:
  * How are the parcels with buildings distributed within the zoning categories?
  * How are the parcels distributed: parcel area x area ratio x lot size category x zoning?
  
```{r explore-parcel-area-2d-density-zoning-count, message = FALSE}

inv %>% filter(BLDG_LGL) %>% count(ZONING_TYPE, sort = TRUE) %>% print(n=Inf)

```

```{r explore-parcel-area-2d-density-zoning-plot, message = FALSE}

inv_bldg <- inv %>% 
  filter(BLDG_LGL)

gg3 <- ggplot(data = inv_bldg, mapping = aes(x = SUIT_PARCEL_AREA, y = SUIT_PARCEL_AREA_RATIO))
gg3 <- gg3 + geom_bin2d()
gg3 <- gg3 + geom_density2d(color = "orange", alpha = .25)
gg3 <- gg3 + scale_x_sqrt() 
gg3 <- gg3 + facet_grid(ZONING_TYPE ~ AREA_CITY_BLOCK_DETAIL, scales = "free_x")
gg3 <- gg3 + labs(title = "All Parcels", subtitle = "(with buildings)") 

gg3_suit <- ggplot(data = filter(inv_bldg, NEW_SUITABLE_LGL), mapping = aes(x = SUIT_PARCEL_AREA, y = SUIT_PARCEL_AREA_RATIO))
gg3_suit <- gg3_suit + geom_bin2d()
gg3_suit <- gg3_suit + geom_density2d(color = "orange", alpha = .25) 
gg3_suit <- gg3_suit + facet_grid(ZONING_TYPE ~ AREA_CITY_BLOCK_DETAIL, scales = "free_x")
gg3_suit <- gg3_suit + labs(title = "Suitable Parcels", subtitle = "(with buildings)") 

gg3 + gg3_suit + plot_layout(ncol = 1)

```

### What about the outliers?

Exploratory questions:

  * What is the maximum parcel size for outliers and non-outliers?
  * What is the distribution of parcel area x outlier status?
  * What is the distribution of parcel area x parcel area ratio x outlier status?
  * Where are these outliers located? Do they pass the "sniff test" when viewed in a map?
  
```{r explore-parcel-area-outliers, message = FALSE}

inv_out <-list(inv,
     filter(inv, !SUIT_PARCEL_AREA_OUTLIER)) %>% 
    bind_rows(.id = "OUTLIERS") %>% 
    mutate(OUTLIERS_FCT = if_else(OUTLIERS == 1,  "WITH OUTLIERS", "WITHOUT OUTLIERS") ) %>% 
    select(OUTLIERS_FCT, everything())
 

inv_bldg_oversized <- inv %>% 
  filter(BLDG_LGL & as.character(AREA_CITY_BLOCK_DETAIL) %in% "over-sized") %>% 
  transmute(PIN,
            SUIT_PARCEL_AREA, 
            SUIT_PARCEL_AREA_RATIO,
            AREA_CITY_BLOCK_DETAIL,
            AREA_CAT_OUTLIER = is_outlier(sqrt(SUIT_PARCEL_AREA)),
            AREA_CAT_OUTLIER_FCT = if_else(AREA_CAT_OUTLIER, "OUTLIER", "NOT OUTLIER") %>% factor() %>% fct_rev,
            SUIT_PARCEL_AREA)

```

```{r explore-parcel-area-outliers-max, message = FALSE}

inv_bldg_oversized %>% 
  group_by(AREA_CAT_OUTLIER_FCT) %>% 
  summarise(MAX = max(SUIT_PARCEL_AREA))

```
```{r explore-parcel-area-outliers-hist, message = FALSE}

gg5 <- ggplot(data = inv_out, aes(x = SUIT_PARCEL_AREA))
gg5 <- gg5 + geom_histogram()
gg5 <- gg5 + facet_wrap(~ OUTLIERS_FCT, scales = "free_x") 
gg5

```

```{r explore-parcel-area-outliers-2d, message = FALSE}

gg4_os <- ggplot(data = inv_bldg_oversized, mapping = aes(x = SUIT_PARCEL_AREA, y = SUIT_PARCEL_AREA_RATIO))
gg4_os <- gg4_os + geom_bin2d()
gg4_os <- gg4_os + geom_density2d(color = "orange", alpha = .25) 
gg4_os <- gg4_os + facet_wrap(~ AREA_CAT_OUTLIER_FCT, scales = "free_x")
gg4_os

```

```{r explore-parcel-area-outliers-map, eval = FALSE}

inv_bldg_oversized_sf <- inv_bldg_oversized %>% 
  inner_join(parcel_sf_ready, by = "PIN") %>% 
  st_sf %>% 
  st_set_geometry("geometry") %>% 
  select_if(not_sfc)

mapview(inv_bldg_oversized_sf, zcol = "AREA_CAT_OUTLIER_FCT")

```


```{r explore-parcel-area-outliers-map2, eval = FALSE}


inv_sf <- inv %>% 
  filter(SUITABLE_LGL) %>% 
  mutate_if(is.logical, as.factor) %>%  
  inner_join(parcel_sf_ready, by = "PIN") %>% 
  st_sf %>% 
  st_set_geometry("geometry") %>% 
  select_if(not_sfc)

mapview(inv_sf, zcol = "SUIT_PARCEL_AREA_OUTLIER", legend = TRUE)

```




 

