--- 
always_allow_html: yes
editor_options:
  chunk_output_type: console
output:
  html_document:
    df_print: paged
---

```{r make-kc-parcels-not-taxed-setup,warning=FALSE, echo=FALSE, message=FALSE}
library(tidyverse)
library(stringr)
library(sf)
library(googledrive)
library(miscgis)
library(forcats)
library(leaflet)
library(mapview)
library(miscgis)
library(snakecase)
library(magrittr)
library(rprojroot)
library(knitr)
library(skimr)

root <- rprojroot::is_rstudio_project
root_file <- root$make_fix_file()
options(httr_oob_default=TRUE) 
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

#### Description {-}

A dataset of parcels within King County, Washington. Each record in this datatset is not currently paying taxes - a status which _may_ make them a suitable candidate for the development of affordable housing and early learning facilities.

This data reflects the King County Assessor records as of `October 13, 2017`.

#### Summary {-}

```{r  make-kc-parcels-not-taxed-01, eval = TRUE, echo = FALSE, max.print = 10}

tax_0_sf_fp <- root_file("./1-data/3-interim/tax_0_sf_20171013.gpkg")

tax_0_sf <- 
  make_or_read(tax_0_sf_fp,
               {
                 dr_id <- as_id("0B5Pp4V6eCkhrdUh5ZmlGcFpQNzg")
                 
                 drive_read(dr_id = dr_id,
                            path = tax_0_sf_fp,
                            read_fun = st_read,
                            .tempfile = FALSE,
                            quiet = TRUE, 
                            stringsAsFactors = TRUE)
               },
               {st_read(tax_0_sf_fp, quiet = TRUE, stringsAsFactors = TRUE)})

set.seed(20171013)
tax_0_sf %>%
  mutate_at(c("PIN","ACCT_NBR","PROP_NAME"), as.character) %>%
  mutate_if(is.factor, as.character) %>% 
  group_by(TAX_STATUS, TAX_REASON) %>% 
  filter(APPR_LAND_VAL>0 & APPR_IMPS_VAL>0) %>% 
  sample_n(1) %>% 
  st_drop_geometry() 

```

#### Links {-}
  - Sources
    - [King County Assessor Data Download <i class="fa fa-external-link"></i>](http://info.kingcounty.gov/assessor/DataDownload/default.aspx)
    - [King County GIS Portal <i class="fa fa-external-link"></i>](http://www5.kingcounty.gov/gisdataportal/)
  - Datasets
    - [Parcel (tabular) <i class="fa fa-download"></i>](http://aqua.kingcounty.gov/extranet/assessor/Parcel.zip)
    - [Parcel (spatial) <i class="fa fa-download"></i>](ftp://ftp.kingcounty.gov/gis-web/GISData/parcel_SHP.zip)
    - [Real Property Account <i class="fa fa-download"></i>](http://aqua.kingcounty.gov/extranet/assessor/Real%20Property%20Account.zip)
  - Metadata
    - [Parcel (tabular) <i class="fa fa-download"></i>](http://info.kingcounty.gov/assessor/datadownload/desc/Parcel.doc)
    - [Parcel (spatial) <i class="fa fa-external-link"></i>](http://www5.kingcounty.gov/sdc/Metadata.aspx?Layer=parcel)
    - [Real Property Account <i class="fa fa-download"></i>](http://info.kingcounty.gov/assessor/datadownload/desc/Real%20Property%20Account.doc)

#### Processing Steps {-}
##### Summary {-}
  1.  Create `p`: a `tibble` containing parcel data for the entire county.
  2.  Create `acct`: a `tibble` containing real property account data for the entire county.
  3.  Create `p_sf`: a `simple feature` object containing the spatial polygon representations of each parcel in the county-wide dataset.
  4.  Clean/process the three dataset: prepare the datasets to be joined and filtered.
    - Load `tax_status` and `tax_reason` for transforming coded features into descriptive text.
  5.  Create `tax_0_sf`: Join and filter the datasets.
    - Join with `inner_join()` to ensure that only records common to all three datasets are retained (note: this action may implicitly filter the data)
    - Filter by excluding records whose `TAX_STATUS` is `Taxable`.
  6. Upload to Drive

##### Step 1 {-}
```{r make-kc-parcels-not-taxed-02, echo = TRUE, eval = FALSE, message=FALSE}
p_fp <- root_file("./1-data/2-external/EXTR_Parcel_20171013.csv")


p_load <- 
  make_or_read(p_fp,
               {
                 zip_dir <- root_file("./1-data/2-external")
                 
                 target_name <- "EXTR_Parcel_20171013.csv"
                 
                 dr_id <- as_id("0B5Pp4V6eCkhraF9jOTl3bURiMkU")
                 
                 drive_read_zip(
                   dr_id = dr_id,
                   .tempdir = FALSE,
                   dir_path = zip_dir,
                   read_fun = read_csv,
                   target_name = target_name
                 ) 
               },
               {
                 read_csv(p_fp)
               }) 


p <- 
  p_load %>% 
  rename_all(to_screaming_snake_case) 

rm(p_load)
gc(verbose = FALSE)

```


##### Step 2 {-}
```{r make-kc-parcels-not-taxed-03, echo = TRUE, eval = FALSE, warning = FALSE}
acct_fp <- root_file("./1-data/2-external/EXTR_RPAcctl_20171013.csv")

acct_load <- 
  make_or_read(acct_fp,
               {
                 dr_id <- "0B5Pp4V6eCkhreGt2djZCTnFUeFU"
                 
                 zip_dir <- root_file("./1-data/2-external")
                 
                 target_name <- "EXTR_RPAcctl_20171013.csv"
                 
                 drive_read_zip(dr_id = dr_id,
                                .tempdir = FALSE,
                                dir_path = zip_dir,
                                read_fun = read_csv,
                                target_name = target_name)
                 
               },
               {read_csv(acct_fp)}) 

rm(acct_load)
gc(verbose = FALSE)

```

##### Step 3 {-}

```{r make-kc-parcels-not-taxed-04, eval = FALSE, echo = TRUE}
p_sf_fp <- root_file("./1-data/2-external/parcel")

p_sf_load <- 
  make_or_read(p_sf_fp,
               {
                 dr_id <- "0B5Pp4V6eCkhrRnM4bHFmWTBTQnM"
                 
                 zip_dir <- root_file("./1-data/2-external")
                 
                 target_name <- "parcel"
                 
                 drive_read_zip(dr_id = dr_id,
                                dir_path = zip_dir,
                                read_fun = st_read,
                                target_name = target_name,
                                .tempdir = FALSE,
                                layer = "parcel",
                                stringsAsFactors = FALSE)
               },
               {st_read(p_sf_fp, layer = "parcel", stringsAsFactors = FALSE)})

p_sf <-
  p_sf_load %>%
  rename_if(not_sfc, to_screaming_snake_case)

rm(p_sf_load)
gc(verbose = FALSE)

```

##### Step 4 {-}

```{r make-kc-parcels-not-taxed-05, eval = FALSE, echo = TRUE}

tr_fp <- root_file("./1-data/3-interim/kc-tax-reason.rds")

tax_reason <- 
  make_or_read(tr_fp,
               {
                 dr_id <- as_id("0B5Pp4V6eCkhrQzdjY0hKVUhOR3M")
                 
                 drive_read(dr_id = dr_id,
                            .tempfile = FALSE,
                            path = tr_fp,
                            read_fun = read_rds)
                 
               },
               {read_rds(tr_fp)})

ts_fp <- root_file("./1-data/3-interim/kc-tax-status.rds")

tax_status <- 
  make_or_read(ts_fp,
               {
                 dr_id <- as_id("0B5Pp4V6eCkhrWFlYLWM3RC1pRDA")
                 
                 drive_read(dr_id = dr_id,
                            .tempfile = FALSE,
                            path = ts_fp,
                            read_fun = read_rds)
                 
               },
               {read_rds(ts_fp)})

p_ready <- 
  p %>% 
  mutate(PIN = str_c(MAJOR, MINOR)) %>% 
  select(PIN,
         PROP_NAME,
         PROP_TYPE,
         DISTRICT_NAME,
         CURRENT_ZONING,
         PRESENT_USE,
         SQ_FT_LOT,
         ACCESS,
         TOPOGRAPHY,
         RESTRICTIVE_SZ_SHAPE,
         PCNT_UNUSABLE,
         CONTAMINATION,
         HISTORIC_SITE,
         EASEMENTS,
         SEISMIC_HAZARD,
         LANDSLIDE_HAZARD,
         STEEP_SLOPE_HAZARD 
  )


acct_frmt <- 
  acct %>% 
  mutate(PIN = str_c(MAJOR,MINOR),
         TAX_STATUS = tax_status[TAX_STAT],
         TAX_REASON = tax_reason[TAX_VAL_REASON]) %>% 
  select(PIN, 
         ACCT_NBR,
         BILL_YR,
         TAX_STATUS,
         TAX_REASON,
         APPR_LAND_VAL,
         APPR_IMPS_VAL,
         TAXABLE_LAND_VAL,
         TAXABLE_IMPS_VAL)

acct_ready <- 
  acct_frmt %>% 
  miscgis::subset_duplicated("PIN") %>% 
  group_by(PIN) %>% 
  drop_na %>% 
  ungroup %>% 
  bind_rows(subset_duplicated(acct_frmt,"PIN",notin = TRUE)) %>% 
  arrange(PIN)

p_sf_ready <- 
  select(p_sf, PIN)

```


##### Step 5 {-}

```{r make-kc-parcels-not-taxed-06, eval = FALSE, echo = TRUE}

tax_0_sf <- 
  list(acct_ready,p_ready,p_sf_ready) %>% 
  reduce(.f = inner_join, by = "PIN") %>%   # Filter: inner_join()
  filter(TAX_STATUS %!in% "Taxable") %>%    # Filter: TAX_STATUS %!in% "Taxable"
  st_as_sf()

```


##### Step 6 {-}

```{r make-kc-parcels-not-taxed-07, eval = FALSE, echo = TRUE}

tax_0_fp <- "./1-data/3-interim/tax_0_sf_20171013.gpkg"

st_write(tax_0_sf,dsn = tax_0_fp, driver = "GPKG")

drive_folder <- as_id("0B5Pp4V6eCkhrZ3NHOEE0Sl9FbWc")

drive_upload(tax_0_fp, path = drive_folder)
