--- 
always_allow_html: yes
editor_options:
  chunk_output_type: console
output:
  html_document:
    df_print: default
  html_notebook:
    code_folding: hide
---

```{r make-kc-lookup-intro-setup, warning=FALSE, echo=FALSE, message=FALSE}

library(tidyverse)
library(stringr)
library(sf)
library(googledrive)
library(miscgis)
library(forcats)
library(leaflet)
library(mapview)
library(miscgis)
library(htmltools)
library(snakecase)
library(magrittr)
library(rprojroot)
library(knitr)
root <- rprojroot::is_rstudio_project
root_file <- root$make_fix_file()
options(httr_oob_default=TRUE) 
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

####Introduction {-}

A set of named lists that allow King County's various codifications to be converted into 
clearer text.

For example, the following abbreviations are used to indicate the `tax status` of a parcel:

```{r make-kc-lookup-intro-01, echo = FALSE, eval = TRUE}

tibble::tribble(
  ~ABBREVIATION,    ~CATEGORY,
            "T",    "Taxable",
            "X",     "Exempt",
            "O",  "Operating"
  ) %>% knitr::kable("html") 

```

Most lookup codes are contained in the metadata that Kign County provides for each dataset. They are usually presented in the following format: `T = Taxable; X = Exempt; O = Operating`

The following function is used to parse a string formatted this way:

```{r make-kc-lookup-intro-02, echo = TRUE, eval = FALSE, warning=FALSE} 

parse_lookup_string <- function(string, col_sep, row_sep){
  str_split(string, pattern = row_sep) %>% 
    flatten() %>% 
    keep(~ str_detect(.x,"")) %>%  
    str_replace_all("\\\n","") %>% 
    map_chr(c) %>% 
    map_df(~.x %>% str_split(pattern = col_sep) %>% as.data.frame %>% t %>% as_data_frame ) %>%  
    set_rownames(NULL) %>% 
    mutate_all(as.character) %>%  
    pmap(~ set_names(..2, ..1)) %>% 
    unlist()
}

```

```{r make-kc-lookup-intro-03, echo = TRUE, warning=FALSE} 
string <- 
"
T = Taxable; X = Exempt; O = Operating
"

tax_reason_named_list <- parse_lookup_string(string, col_sep = "\\s=\\s",row_sep = ";\\s") 
```


The named list objects created in this section are used to de-code the various codification schemes
used in the King County data. A code value is passed to the named list and the corresponding category or description is returned: 

```{r make-kc-lookup-intro-04, echo = TRUE, warning=FALSE} 

# Option 1
code_value <- "X"

tax_reason_named_list[code_value]

# Option 2
tax_reason_named_list["O"]
```
