--- 
always_allow_html: yes
editor_options:
  chunk_output_type: console
output:
  html_document:
    df_print: paged
---

```{r make-kc-lookup-tax-status-setup,warning=FALSE, echo=FALSE, message=FALSE}
library(tidyverse)
library(stringr)
library(sf)
library(googledrive)
library(miscgis)
library(forcats)
library(leaflet)
library(mapview)
library(miscgis)
library(snakecase)
library(magrittr)
library(rprojroot)

root <- rprojroot::is_rstudio_project
root_file <- root$make_fix_file()
options(httr_oob_default=TRUE) 
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

### King County Tax Status

#### Description {-}

The status of the parcel's taxation. The categories are: `Taxable`,`Exempt`, or `Operating`. 


#### Links {-}
  - [Source <i class="fa fa-external-link"></i>](http://info.kingcounty.gov/assessor/DataDownload/default.aspx)
  - [Data <i class="fa fa-external-link"></i>](http://info.kingcounty.gov/assessor/datadownload/desc/Real%20Property%20Account.doc)

#### Processing Steps {-}
##### Summary {-}
  1.  Create `string`: The contents of the Real Property Account metadata table pasted into the R environment.
  2.  Create `tax_reason`: Pass `string` to the `parse_lookup_string()` function.
  3.  Upload `tax_reason` to Google Drive.
  
##### Step 1 {-}
```{r make-kc-lookup-tax-status-01, echo = TRUE, message=FALSE}
string <- "
T = Taxable; X = Exempt; O = Operating
"

```


##### Step 2 {-}
```{r make-kc-lookup-tax-status-02, echo = TRUE, warning = FALSE}

tax_status <- 
  string %>% 
  parse_lookup_string(col_sep = "\\s=\\s", row_sep = ";\\s")

data.frame(DESCRIPTION = tax_status) %>% kable(format = "html")
```

##### Step 3 {-}

```{r make-kc-lookup-tax-status-03, eval = FALSE, echo = TRUE}
folder <- as_id("0B5Pp4V6eCkhrZ3NHOEE0Sl9FbWc")

tmp <- tempfile()

write_rds(tax_status,tmp)

drive_upload(tmp, folder,name = "kc-tax-status.rds",)
```
