--- 
always_allow_html: yes
editor_options:
  chunk_output_type: console
output:
  html_document:
    df_print: paged
---

```{r make-kc-lookup-presuse-setup,warning=FALSE, echo=FALSE, message=FALSE}
library(tidyverse)
library(stringr)
library(sf)
library(googledrive)
library(miscgis)
library(forcats)
library(leaflet)
library(mapview)
library(miscgis)
library(htmltools)
library(snakecase)
library(magrittr)
library(rprojroot)

root <- rprojroot::is_rstudio_project
root_file <- root$make_fix_file()
options(httr_oob_default=TRUE) 
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

### King County Present Use Categories

####Description {-}

_Description text here_


####Links: {-}
  - [Source <i class="fa fa-external-link"></i>](http://www5.kingcounty.gov/gisdataportal/)
  - [Data <i class="fa fa-external-link"></i>](ftp://ftp.kingcounty.gov/gis-web/GISData/public_parcels_SHP.zip)
  - [Metadata <i class="fa fa-external-link"></i>](http://www5.kingcounty.gov/sdc/Metadata.aspx?Layer=public_parcels)

#### Processing Steps {-}
##### Summary {-}
  1. Create `pu_ready`: A lookup list of present use categories and their 2-character codes
  2. Load `juris`: A named vector of the jurisdictions and their abbreviations.
  3. _Insert third step_
  
##### Step 1 {-}
```{r make-kc-lookup-presuse-01, echo = TRUE, message=FALSE}

pu_fp <- root_file("./1-data/2-external/EXTR_LookUp.csv")

maybe_make(pu_fp,{
  dr_id <- "0B5Pp4V6eCkhrN212NEFOeVV6T2s"
  
  d <- drive_get(id = dr_id)
  
  tmp <- tempfile()
  
  d %>% drive_download(path = tmp)
  
  unzip_dir <- root_file("./1-data/2-external")
  
  unzip(zipfile = tmp,exdir = unzip_dir)
})

pu_ready <- 
  read_csv(pu_fp) %>%
  rename_all(to_screaming_snake_case) %>% 
  filter(LU_TYPE %in% 102) %>% 
  select(LU_DESCRIPTION, LU_ITEM) %>% 
  pmap(~purrr::set_names(..1,..2))


```


##### Step 2 {-}
```{r make-kc-lookup-presuse-02, echo = TRUE}

juris_fp <- root_file("./1-data/3-interim/kc-jurisdictions.rds")

maybe_make(juris_fp, {
  
  dr_id <- as_id("0B5Pp4V6eCkhrTU9Kd3hVVVkyZjQ")
  
  d <- drive_get(dr_id)
  
  d %>% drive_download(path = juris_fp) 
  
})

juris <- read_rds(juris_fp)


```


